---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(mrdrivers) # nolint
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- # mrdrivers -->

<!-- badges: start -->

<!-- [![lucode2-check](https://github.com/pik-piam/mrdrivers/actions/workflows/lucode2-check.yaml/badge.svg)](https://github.com/pik-piam/mrdrivers/actions/workflows/lucode2-check.yaml) -->

<!-- [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-bright_green.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable) -->

<!-- [![Codecov test coverage](https://codecov.io/gh/pik-piam/mrdrivers/branch/main/graph/badge.svg)](https://app.codecov.io/gh/pik-piam/mrdrivers?branch=main) -->

<!-- badges: end -->

<!-- The goal of **mrdrivers** is to handle the construction of GDP, GDP per capita, Population and Urban Population share scenarios: all of which are important drivers to the REMIND and MAgPIE models. -->

<!-- ## Installation -->

<!-- ```{r, eval=FALSE} -->

<!-- # From the PIK rse-server -->

<!-- install.packages("mrdrivers", repos = "https://rse.pik-potsdam.de/r/packages") -->

<!-- # or from Github -->

<!-- remotes::install_github("pik-piam/mrdrivers") -->

<!-- ``` -->

## Framework

This package depends upon the [madrat](https://github.com/pik-piam/madrat#readme) and [magclass](https://github.com/pik-piam/magclass#readme) packages. It integrates into the madrat framework and is structured accordingly. It mainly uses magpie objects (from the magclass package). For more information on madrat or magclass, please visit the respective github repositories ([madrat](https://github.com/pik-piam/madrat#readme), [magclass](https://github.com/pik-piam/magclass#readme)).

## Functions

The key `madrat::readSource()` and `madrat::calcOutput()` functions provided by this package are listed below.

readSource:

```{r, echo=FALSE}
c("readSSP", "readWDI", "readIMF", "readUN_PopDiv", "readPEAP")
```

calcOutput:

```{r, echo=FALSE}
c("calcGDP", "calcGDPpc", "calcPopulation", "calcLabour", "calcUrban", "calcRatioPPP2MER")
```

## Scenarios

The current default scenarios returned for all drivers (i.e. GDP, GDP per capita, Population, Labour, and Urban Population Share) are:

-   the SSPs, i.e. SSP1-5

-   the SDPs, i.e. SDP, SDP_EI, SDP_MC and SDP_RC

see `vignette("scenarios")` for more information on available scenarios and references of the default scenarios.
